The \dealii Library, Version 9.6

### 2024-09-23 9.6/paper.tex
add my todo list

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relicensing to Apache 2.0}\label{sec:license}

\todo[inline]{Matthias: Where are we with this, and what of it is
  worth describing here?}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relicensing to Apache License 2.0 with LLVM exception}
\label{sec:license}

\color{red}
\begin{itemize}
  \item
    Motivation for license change, goals: make contributions from industry
    possible / improve deal.II adoption. Mention reasons against LGPL 2.1,
    Explaing why GPL-3/LGPL-3 is not a good fit. Explain why Apache 2.0
    with LLVM exception.
  \item
    Successful examples LLVM and Kokkos (with same license)
  \item
    Status of external collaborators
  \item
    Approach: Require all new contributions to be dual licensed
\end{itemize}
\color{black}
